The transboundary nature of the world’s exploited marine species

### 2020-10-06 Scripts/Manuscript_Draft.Rmd
Figures size for thesis

### Materials and Methods

@@

```{r Figure1, eval = T, fig.width=12, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and their contribution to global fisheries catch and revenue. a) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively. b) Contribution of transboundary species to regional revenue (left) and catch (right). Regions classified according to the United Nations sub-regions. Points = mean +- sd. Revenue in 2010 real USD"}

@@

```{r Figure2, eval = T, fig.width=8, fig.height=6, echo=FALSE, fig.pos= "H", fig.cap=""}

@@

```{r Figure3, eval = T, fig.width=12, fig.height=12, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch category. Category A, increasing catch; Category B, constant catch; Category C, decreasing catch"}

@@

<!-- ![Figure 3. Number of transboundary species by catch trend and EEZ. Category A, Increasing; Category B, Constant; Category C, Decreasing. “No Category” reflects species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data. Figure created using R version 3.5.2.](../Figures/Fig3.png) -->

@@

```{r Figure4, eval = T, fig.width=12, fig.height=14, echo=FALSE, fig.pos= "H", fig.cap="Number of countries shared by transboundary species. Showing only species that share > 20 countries"}

@@

<!-- ![Figure 4. Number of EEZs shared by transboundary species. a) Number of EEZs by species organized according to ecosystem preference as defined by FishBase. Showing only species that share > 20 EEZs. b) Average catch between 2005 and 2014 for top five countries capturing the top five shared species for each ecosystem preference category (color coding is as shown in legend in a). Note that there could be > 5 species due to similar sharing values. The category “Other” consists of species that have no ’ecosystem preference’ classification in FishBase. Figure created using R version 3.5.2.](../Figures/Fig4.png) -->

@@

## References

<div id="refs"></div>

>>>>

### Materials and methods

@@

```{r Figure1, eval = T, fig.width=12, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species and their contribution to global fisheries catch and revenue. a) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively. b) Contribution of transboundary species to regional revenue (left) and catch (right). Regions classified according to the United Nations sub-regions: E. = Eastern, N. = Northern, S. = Southern, W. = Western, Ltn. Ame. & the Car. = Latin America and the Caribbean. Points = regional  mean \u00B1 sd. Revenue in 2019 real USD."}

@@

```{r Figure2, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Weighted benefits of transboundary species by km^2$ and UN sub-region. a) Revenue in thousand 2019 USD. b) Catch in tonnes. Points are sub-region averages \u00B1 s.d. by country."}

@@

```{r Figure3, eval = T, fig.width=12, fig.height=12, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by catch trend and EEZ. Category A, Increasing; Category B, Constant; Category C, Decreasing. “No Category” reflects species with less than 10 years of catch data and/ or less than 5 consecutive years of catch data."}

@@

@@

```{r Figure4, eval = T, fig.width=12, fig.height=14, echo=FALSE, fig.pos= "H", fig.cap="Number of EEZs shared by transboundary species. a) Number of EEZs by species organized according to ecosystem preference as defined by FishBase. Showing only species that share > 20 EEZs. b) Average catch between 2005 and 2014 for top five countries capturing the top five shared species for each ecosystem preference category (color coding is as shown in legend in a). Note that there could be > 5 species due to similar sharing values. The category “Other” consists of species that have no ’ecosystem preference’ classification in FishBase."}

@@

@@

<!-- ## References -->

<!-- <div id="refs"></div> -->
